### 2016-12-06 paper/chapters/sigmoid_belief_nets.tex
added tikz picture for sbn node

\section{Sigmoid Belief Networks}
\label{sec:sbn}
Sigmoid Belief Networks (SBN) have been proposed in 1992 by R.M. Neal \cite{neal:1992} representing a a specific type of bayesian networks \cite{pearl:1985}.
They are one of the earliest neural networks used for generative modelling, predating all other presented models in this article.
In its most common form, SBNs are comprised by a number of layers where each node in a layer is a sigmoid function of its ancestors:
$$
p(s_i) = \sigma\bigg(\sum_{j<i}W_{j,i}s_j+b_i\bigg)
$$

>>>>

\section{Sigmoid Belief Networks}
\label{sec:sbn}
Sigmoid Belief Networks (SBN) have been proposed in 1992 by R.M. Neal \cite{neal:1992} representing a a specific type of bayesian networks \cite{pearl:1985}.
They are one of the earliest neural networks used for generative modelling, predating all other presented models in this article.

These random variables are interpreted in a bayesian way where each one may be observed, hidden (or latent) or unknown representing different states of knowledge or belief \cite{definetti:1974}.

\begin{figure}[htb]
\centering
\input{media/sbn_node.tikz}
  \caption{VAE architecture (source: VAE paper)}\label{fig:vae_architecture}
\end{figure}
In its most common form, SBNs are comprised by a number of layers where each node in a layer is a sigmoid function of its ancestors:
$$
p(s_i) = \sigma\bigg(\sum_{j<i}W_{j,i}s_j+b_i\bigg)
$$
